---
title: "Visalimbo"
author: "parthkhare"
date: 2022-07-05T21:13:14-05:00
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(data.table);library(readxl);library(ggplot2); library(countrycode)
```

### Visa wait times

Coivd lockdowns are more or less over. With almost 70% of global population [vaccinated](%22https://www.nytimes.com/interactive/2021/world/covid-vaccinations-tracker.html%22), most countries have opened their borders. But can anyone really travel ? The waiting times to get any category of visa is unimaginable long. 
The following analysis based on wait time from the [US Department of State](https://travel.state.gov/content/travel/en/us-visas/visa-information-resources/wait-times.html) illustrates this further.


### Delays in visiting visa wait time extent upto 3 years!
```{r, echo=FALSE, warning=FALSE, message=F}
# Scraped Data Stats
# --------------
scpdt_base <- read.csv('/Users/moonlight/Documents/Moonlight Projects/2022/Visa Limbo/Data/visascraped_base_mapped.csv')
scpdt_base$X <- NULL
scpdt_base <- data.table(scpdt_base)
scpdt_base$ctyname <- countrycode(scpdt_base$Country, origin = 'iso3c', destination = 'country.name')

# ------------------------
# Charts: most delayed countries
# ------------------------
# Aggregate delay by countries
scpdt_cty <- scpdt_base[,.(VisitorVisa = mean(VisitorVisa, na.rm=T),
                        Student_ExchangeVisitorVisas=mean(Student_ExchangeVisitorVisas, na.rm=T),
                        AllOtherNonimmigrantVisas=mean(AllOtherNonimmigrantVisas,na.rm=T)),
                        by = .(Country,ctyname, date)]


# ----------------------------------------
# Charts for all visa types separately
# ----------------------------------------
# Visitor Visa more than one year
ggplot(scpdt_cty[scpdt_cty$VisitorVisa>365,], aes(y=reorder(ctyname,VisitorVisa), x=VisitorVisa)) +
  geom_bar(fill='red',stat='identity') + ggtitle("US Visa Waitime: Visitor Visa > 1 year") +  
  theme_minimal() + theme(axis.text.x=element_text(angle=90,hjust=1))+ ylab('Country') +
  xlab('Waitime by country in days')

```

### The lag is consistent across all visa categories

```{r scpdt_cty, echo=FALSE, warning=FALSE}
# Charts for all visa types combined
# ----------------------------------------
# reshape data
scpct_res <- melt(scpdt_cty, measure.vars = c( "VisitorVisa","Student_ExchangeVisitorVisas","AllOtherNonimmigrantVisas"),
               variable.name = "Visatype", value.name = "Waittime_days")

# CI: remove or keep countries
keep_cty <- c('ARM','JOR','PAN','KEN','BGD','GHA','TUR','NGA','BRB','GUY','ETH','JAM','MKD','COL','COD','ESP','KGZ','ISR','ARE','IRQ','GRC','URY','DOM','VEN','CHL','ECU','CRI','DJI','AUS','CAN','MNG','MEX','BEN','ARG','FIN','SEN','XXR','PAK','BFA','NLD','FRA','PER','IND','LBR','CZE','MLT','UGA','EGY')

# CI: geom bar for all countries
ggplot(scpct_res[scpct_res$Country %in% keep_cty],
       aes(x=reorder(Country,-Waittime_days),y=Waittime_days,fill=Visatype)) +
  geom_bar(stat='identity') + ggtitle("US Visa Waitime") +  
  theme_minimal() + theme(axis.text.x=element_text(angle=90,hjust=1))+ xlab('Country') +
  ylab('Waitime in days by country (avg across Embassies)')
```
