---
title: "VisaLimbo"
author: "parthkhare"
date: 2022-07-05T21:13:14-05:00
# categories: ["R"]
# tags: ["Immigration", "Visa", "Embassy"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
library(data.table);library(readxl);library(ggplot2); library(countrycode)
```

### Visa wait times
Coivd lockdowns are more or less over. With almost 70% of global population [vaccinated](%22https://www.nytimes.com/interactive/2021/world/covid-vaccinations-tracker.html%22), most countries have opened their borders. But can anyone really travel ? The waiting times to get any category of visa is unimaginably long. 


Based on State Department [data](https://travel.state.gov/content/travel/en/us-visas/visa-information-resources/wait-times.html), the following post analyses visa wait times for 237 embassies across 172 countries. There results are shown for three categories, Visitor Visa, Student/Exchange Visitor Visas and All Other Non-immigrant visa. 


Delay for Visitor visas is the highest, based on July, 2022 average delay is around 237 days. Following embassies currently have visitor's visa wait time for over 1 year

```{r, echo=FALSE, warning=FALSE, message=F}
# Scraped Data Stats
# --------------
scpdt_base <- read.csv('/Users/moonlight/Documents/Moonlight Projects/2022/Visa Limbo/Data/visascraped_base_mapped.csv')
scpdt_base$X <- NULL
scpdt_base <- data.table(scpdt_base)
scpdt_base$ctyname <- countrycode(scpdt_base$Country, origin = 'iso3c', destination = 'country.name')

# ----------------------------------------
# Charts for all visa types separately
# ----------------------------------------
# Visitor Visa more than one year
ggplot(scpdt_base[scpdt_base$VisitorVisa>365,], aes(y=reorder(Embassy,VisitorVisa), 
                                                  x=VisitorVisa)) +
  geom_bar(fill='red',stat='identity') + ggtitle("Visitor Visa > 1 year") +  
  theme_minimal() + ylab('Emabssy') + xlab('Waitime (days)') +
  theme(axis.text=element_text(size=rel(0.7)))

```

Average delay for Student/Exchange Visitor Visas is 46 days, following are the embassies with maximum lags
```{r scpdt_base, echo=FALSE, warning=FALSE, message=F}

# Charts for all visa types separately
# ----------------------------------------
# Visitor Visa more than one year
ggplot(scpdt_base[scpdt_base$Student_ExchangeVisitorVisas>60,], aes(y=reorder(Embassy,Student_ExchangeVisitorVisas), 
                                                  x=Student_ExchangeVisitorVisas)) +
  geom_bar(fill='darkgreen',stat='identity') + ggtitle("Student/Exchange Visitor Visas") +  
  theme_minimal() + ylab('Emabssy') + xlab('Waitime (days)') +
  theme(axis.text=element_text(size=rel(0.7)))
```



Average delay for All Other Non-immigrant Visas is 68 days, following are countries with longest delays
```{r, echo=FALSE, warning=FALSE, message=F}
# Scraped Data Stats
# --------------


# ----------------------------------------
# Charts for all visa types separately
# ----------------------------------------
# Visitor Visa more than one year
ggplot(scpdt_base[scpdt_base$AllOtherNonimmigrantVisas>100,], aes(y=reorder(Embassy,AllOtherNonimmigrantVisas), 
                                                  x=AllOtherNonimmigrantVisas)) +
  geom_bar(fill='darkblue',stat='identity') + ggtitle("All Other Nonimmigrant Visas") +  
  theme_minimal() + ylab('Emabssy') + xlab('Waitime (days)') +
  theme(axis.text=element_text(size=rel(0.7)))
```





<!-- The lag is consistent across all visa categories -->
<!-- ```{r scpdt_cty, echo=FALSE, warning=FALSE} -->
<!-- # Charts for all visa types combined -->
<!-- # ---------------------------------------- -->
<!-- # reshape data -->
<!-- scpct_res <- melt(scpdt_cty, measure.vars = c( "VisitorVisa","Student_ExchangeVisitorVisas", -->
<!--                                                "AllOtherNonimmigrantVisas"), -->
<!--                   variable.name = "Visatype", value.name = "Waittime_days") -->
<!-- scpct_res <- scpct_res[!is.na(scpct_res$Waittime_days),] -->

<!-- # Subset top countries manually -->
<!-- rem_cty <- c('Papua New Guinea','Micronesia (Federated States of)','Timor-Leste','Poland', -->
<!--              'Burundi','Hong Kong SAR China','Brunei','Bosnia & Herzegovina','Cambodia', -->
<!--              'Latvia','Angola','Eritrea','Fiji','Chad','Suriname','Curaçao','Turkmenistan', -->
<!--              'Oman','Mali','Trinidad & Tobago','Senegal','Eswatini','Equatorial Guinea', -->
<!--              'Gabon','Togo','Madagascar','Benin','Guatemala','Cape Verde','Sierra Leone', -->
<!--              'Mauritania','Kuwait') -->
<!-- scpct_sub <- scpct_res[!scpct_res$ctyname %in% rem_cty,] -->


<!-- # CI: geom bar for all countries -->
<!-- ggplot(scpct_sub,aes(x=reorder(ctyname, Waittime_days, FUN=sum),y=Waittime_days/7.019)) +  -->
<!--   geom_bar(stat='identity', aes(fill = Visatype)) + coord_flip() + theme_minimal() +    -->
<!--   ggtitle("US Visa Waitime") +  xlab('Country') + ylab('Waitime (weeks)') +  -->
<!--   facet_grid(cols = vars(Visatype)) +  -->
<!--   theme(axis.text = element_text(family = "Courier", size = (6)), -->
<!--         axis.text.x=element_text(size=rel(0.7)), legend.position="none") -->
<!-- ``` -->


Questions?
Contact: visalimbo@gmail.com












<!-- Average lag by different visa types -->

<!-- ```{r scpdt_base, echo=FALSE, warning=FALSE} -->
<!-- # Average delay across all categories of visa: by embassies -->
<!-- # ---------------------------------------- -->
<!-- scrpie <- scpdt_base[,.(Visitor = mean(VisitorVisa, na.rm=T), -->
<!--                            Student_Exchange_Visitor=mean(Student_ExchangeVisitorVisas, na.rm=T), -->
<!--                            Other_Nonimmigrant=mean(AllOtherNonimmigrantVisas,na.rm=T))] -->

<!-- scrpiedt <-  melt(scrpie, measure.vars = c( "Visitor","Student_Exchange_Visitor", -->
<!--                                             "Other_Nonimmigrant"), -->
<!--                   variable.name = "Visatype", value.name = "Waittime_days") -->

<!-- scrpiedt$prop <-  scrpiedt$Waittime_days/sum(scrpiedt$Waittime_days) -->
<!-- scrpiedt$prop <- scrpiedt$prop*100 -->
<!-- scrpiedt$ypos <- cumsum(scrpiedt$prop)- 0.5*scrpiedt$prop  -->

<!-- # Basic piechart -->
<!-- ggplot(scrpiedt, aes(x="", y=prop, fill=Visatype)) + -->
<!--   geom_bar(stat="identity", width=1, color="white") +  xlab('') +  -->
<!--   coord_polar("y", start=0) + theme_void() + -->
<!--   geom_text(aes(y=prop+3, label = paste0(round(prop,0),'%')), color = "white", size=3) -->
<!-- ``` -->